### 2015-04-12 trunk/documents/thesis/thesis_LO_QT.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,letterpaper,english,12pt,english,openany,letterpaper,pagesize]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{esint}
\onehalfspacing

@@

\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
Meshes}{\huge \par}

@@

\textbf{\large Alexander Pinzón Fernández}{\large \par}

@@

Facultad de Ingenieria, Departamento de Sistemas e Industrial

{\small Grupo de Investigación CIM@LAB}{\small \par}

@@

{\small A thesis submitted in partial fulfillment of the requirements
for the degree of:}{\small \par}

@@

{\small Advisor:}\\
{\small Eduardo Romero Castro , Ph.D.}{\small \par}

{\small \vspace{1.5cm}
}{\small \par}

{\small Research Area:}\\
{\small Computer Graphics}{\small \par}

{\small \vspace{2cm}
}{\small \par}

{\small Universidad Nacional de Colombia}\\
{\small Facultad de Ingenieria, Departamento de Sistemas e Industrial}\\
{\small Grupo de Investigación CIM@LAB}\\
{\small Bogotá, Colombia}\\
{\small 2014}{\small \par}

@@

{\small \vspace{4cm}
}{\small \par}

\noindent \begin{flushright}
\begin{minipage}[t]{8cm}%
{\small A Beatriz y Campo Elias mis padres que siempre me dieron la
libertad de escoger, con su comprensión y apoyo me permitieron dedicar
mi tiempo a la ciencia.}{\small \par}

{\small \vspace{1cm}
}{\small \par}

{\small A mis padres}{\small \par}

{\small \vspace{1cm}
}{\small \par}

@@

Campo Elias Pinzon Rojas%
\end{minipage}
\par\end{flushright}

@@

\textbf{\LARGE Acknowledgement}{\LARGE \par}

\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}

@@

I wold like to thank my advisor professor Eduardo Romero and CIM\&LAB
research group for his support in this thesis.

{\small \vspace{1cm}
}{\small \par}

@@

{\small \vspace{1cm}
}{\small \par}

This work was supported in part by the Blender Foundation, Google
Summer of code program at 2012 - 2013.

@@

\textbf{\LARGE Abstract}{\LARGE \par}

\addcontentsline{toc}{chapter}{\numberline{}Abstract}

In the last two decades three-dimensional modeling methods have been
evolving and developing rapidly, thanks in part to the use of vector
operators of differential geometry. The Laplacian operator has been
one of the most widely studied and used thanks to the properties exhibited
by their eigenvectors in novel applications such as noise reduction,
enhancement, remeshing, UV mapping, posed, skeletonization, among
other. The differential operator is defined in a continuous and smooth
domain named manifold, manifolds are often approximated by discrete
polygon meshes composed by triangles and quadrangles which represent
the real world three-dimensional objects. In these meshes spectral
structure is calculated using a discrete Laplacian operator, the discrete
version of the Laplacian operator given by Pinkall in 1993 works only
with meshes of triangles, and Xiong in 2011 working exclusively with
quads. This thesis proposes an original extension of the Laplacian
operator that allows to work with hybrid meshes composed by triangles
and quadrangles.

Along with the operator, this work presents new sculpting and modeling
applications with base on the enhancement, applications on subdivision
surfaces using smoothing, mesh posing using differential coordinates
and skeletonization using iterative contraction. This series of applications
demonstrates the quality, predictability and flexibility of the proposed
operator.

The proposed operator was successfully used in real production environments
within software Blender how new tools. Currently these tools are available
as open source software.

\textbf{\LARGE Resumen}{\LARGE \par}

En las dos últimas décadas los métodos de modelado tridimensional
han ido evolucionando y desarrollándose rápidamente, en parte gracias
al uso de operadores vectoriales de geometría diferencial. El operador
Laplaciano ha sido uno de los más ampliamente estudiado y usado gracias
a las propiedades exhibidas por sus vectores propios en novedosas
aplicaciones como: reducción de ruido, realce, remallado, mapeo UV,
posado, esqueletonización, entre otras. Este operador diferencial
es definido en un dominio continuo y suave llamado variedad, las variedades
son a menudo aproximadas por mallas discretas de polígonos compuestas
por triángulos y cuadrángulos que a su vez representan objetos tridimensionales
del mundo real. En estas mallas se calcula la estructura espectral
con el uso de algún operador Laplaciano discreto, la versión discreta
del operador Laplaciano propuesta por Pinkall en el 1993 trabaja únicamente
con mallas compuestas por triángulos, y la de Xiong en el 2011 trabaja
exclusivamente con cuadrángulos. Esta tesis propone una extensión
original del Operador Laplaciano que permite trabajar con mallas híbridas
compuestas por triángulos y cuadrángulos.

@@

El operador propuesto fue usado de forma exitosa en ambientes reales
de producción dentro del software Blender como nuevas herramientas.
Actualmente estas herramientas están disponibles como programas de
código abierto.

{\small \vspace{1cm}
}{\small \par}

\textbf{\small Keywords: laplacian operator; smooth; enhance; sculpting;
subdivision surface}{\small \par}

@@

The discrete versions of Laplace Beltrami Operator have been used
in the last years for the develop of new geometric modeling tools.
In the work of Pinkall \cite{Pinkall1993} was introduced the cotangent
version of Laplace operator, that allow to find the minimal surface
when compute a discete harmonic map with the Laplacian operator, this
version has been widely studied and applied in various problems of
computer geometric modeling. The manifolds that are continuous domains
homeomorphic to $\mathbb{R}^{n}$ are represented in computers by
polygon meshes. These polygons are generally composed of triangles
and quadrangles, while work with laplacian operator in this hybrid
composition are not a mathematical challenge, most research uses only
meshes composed by triangles \cite{Pinkall1993,Desbrun1999,Meyer2003,Sorkine2004,Au2008,Belkin2008,Hahne2006},
in other recent studies \cite{Liu2008,Xiong2011} the Laplacian operator
is working exclusively with quadrangles. But in the artistic scope
topology and the way the edges are distributed, the triangle and quadrangles,
directly affects the processes of animation, interpolation, textured,
etc. As discussed by \cite{Mullen2007} who use a manual connection
of a couple of vertices to perform animation processes and interpolation.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles and change the original topology.

Modeling techniques able to generate a variety of realistic shapes,
have been developed \cite{Botsch2006}. Editing techniques have evolved
from affine transformations to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Neverteless
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented applications requires a single parameter that controls the
global curvature, which is used to maintain realistic shapes, creating
a family of different versions of the same object and therefore preserving
the detail of the original model and a realistic appearance.

The shape inflation and shape exaggeration can thus be used as such
brush in the sculpting process, when inflating a shape since current
brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
In contrast, the presented enhance method inflates a mesh by moving
the vertices towards the reverse curvature direction, conserving the
shape and sharp features of the model.

@@

This work presents an extension of the Laplace Beltrami Operator for
hybrid quad/triangle meshes, representing a larger mesh spectrum from
what has been presented so far. The method eliminates the need of
preprocessing and allows preservation of the original topology. Likewise,
along with this operator, it is proposed a method to generate a family
of parameterized shapes, in a robust and predictable way. This method
enables customization of the smoothness and curvature, obtained during
the subdivision surfaces process. Finally, it is proposed a new brush
for inflating the silhouette mesh features in modeling and sculpting.

This work is organized as follows: Chapter \ref{sub:1.1-Related-work}
presents works related to the Laplacian operator, applications in
digital sculpting, deformation, and offsetting methods for polygonal
meshes; In chapter \ref{chap:Mathematical-foundation}, it is described
the theoretical framework of the Laplacian operator for polygon meshes;
In chapter \ref{sec:Proposed-Method}, it is presented the extension
of the Laplacian Operator for hybrid meshes and applications of shape
inflation ,subdivision of surfaces , deformation, skelenotization
and sculpting; finally some Laplacian Operator results, to hybrid
quad/triangle meshes are graphically shown as well as results of the
shape inflation applications in sculpting, subdivision, deformation,
skelenotization and modeling.

\chapter{Related work\label{sub:1.1-Related-work}}

Many tools have been developed for modeling, based on the Laplacian
mesh processing. These different tools preserve the surface geometric
details when using laplacian operators for different processes such
as smoothing, enhancing, free-form deformation, fusion, morphing and
other applications \cite{Ranjan2012}.

@@

Where $N_{1}$is the 1-ring neighboorhood, $\alpha$ and $\beta$
are the opposite angles to edge between vertex $i$ and vertex $j$.
In this work the discretize laplacian operator was used to find the
minimal surface based on minimization energy strategy using the Dirichlet's
energy of the function $u$ over a manifold represented by triangulated
mesh $\Omega$.

@@

Then Taubin works \cite{Taubin1995} for first time treat the problem
of noise reduction in digital poligonal meshes from signal proccessing
point of view. Taubin extends Fourier analysis to signals defined
on polygonal meshes, Taubin observe that Fourier transform is a decomposition
of the signal into an eigenvectors of the Laplacian operator, and
reconstruct the signal with a linear combination of these eigenvectors.
Desbrun works \cite{Desbrun1999} consider the same approach of Taubin,
but Desbrun use a curvature normal ($\bar{\kappa}\mathbf{n}$) based
on cotangen Laplace operator version for noise reduction over a difussion
process. This it's the most important and popular Laplace Beltrami
opertator discretization \cite{Liu2008}, many works for mesh smoothing
and fairing have been developed based on this LBO discretization \cite{Desbrun2000,Meyer2003,Schneider2001,Nealen2006}.

@@

Where $A$ is the area surrounding vertex $i$. This laplacian operator
$L$ was used for reduce the noise in a mesh $X$ over a difussion
process.

The convergence of the Laplace Beltrami operator has been very important
in fields how numerical analysis, given that implications in the simulation
process and geometric partial differentials equations. In the works
of \cite{Xu2004} is established the convergence of several discrete
Laplace Beltrami operators over triangulated meshes with numerical
results that support the theoretical analysis. Over quadrilateral
meshes Liu \cite{Liu2008} presents a discrete Laplace Beltrami Operator
based on a bilinear interpolation and its convergence over this type
of meshes composed only by quads.

In the work of Sorkine \cite{Sorkine2006} the laplacian operator
was used to repose a meshes while preserving geometry details of the
surface. The details was stored in differential coordinates $\delta_{i}$
for every vertex $v_{i}$.

@@

The differential coordinates represents the difference between the
absolut coordinate of $v_{i}$and the center of mass of its immediate
neighboors.

\cite{Gal2009} propose automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characerized by their first
and second order curvature derivatives, see \cite{Ohtake2004}, and
angle-based threshold. Likewise, curves have been also classified
as planar or non-planar, approximated by lines, circles, ellipses
and other complex shapes. In such case, the user defines an initial
change over several features which is propagated towards other features,
based on the classified shapes and the inter-relationships between
them. This method works well with objects that have sharp edges, composed
of basic geometric shapes such as lines, circles or ellipses. However,
the method is very limited when models are smooth since it cannot
find the proper features to edit.

Digital sculpting have been traditionally approached either under
a polygonal representation or a voxel grid-based method. Brushes for
inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
In grid-based sculpting, some other operations have allowed to add
or remove voxels since production of polygonal meshes require a processing
of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
from the difficulty of maintaining the surface details during larger
scale deformations.

In the literature, several studies have described the skeleton extraction
systems and different metrics that identify appropriate methods given
an application specific \cite{Attali2007}. One of the best methods
reported in the literature for the extraction of the skeleton is the
Laplacian smoothing method for its advantages of homotopy representation
and hierarchical connections between parts. The Skeleton extraction
methods permits simplify the dimension of the object preserving the
topological structure \cite{Cornea2007}, Au et. al. \cite{Au2008}
present a skeleton extraction method based on iterative smooothing-contraction,
in this method the several constraints are used to waranty that the
process converge to skeleton formed by branchs and joins, the constraints
based on laplacian operator, the low frequencies of the mesh are preserving
with the use of attractor to original mesh, while the iterative smoothin
process remove high frecuencies.

\chapter{Mathematical foundation\label{chap:Mathematical-foundation}}

This chapter studies basic mathematical foundation on differential
geometry to understand the differential operators and the Laplace
beltrami operator.

The differential geometry studies curvatures and geodesics \cite{Hahne2006}.
The differential operators show a deep relationships betwen the geoemetry
(curvatures, geodesics) and topology of the manifold. This differential
operators are very used in applications on computer geometric modelling
over the last years \cite{Rosenberg1997,Alexa2011}.

@@

This work is related to manifolds that represent a surface in an three-dimensional
Eucliddean Space. This manifolds are homeomorphic to $\mathbb{R}^{2}$.

The manifols are represented by polygonal meshes with points connected
by triangles and quads.

@@

@@

Triangle and quad configurations of the 1-ring neighborhood faces,
adjacent to $v_{i}$, can be simplified to five cases, as shown in
figure \ref{fig:LBO-basic-5-TQ}.

>>>>

%% LyX 2.1.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,letterpaper,english,12pt,english,openany,letterpaper,pagesize]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{float}
\usepackage{textcomp}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{esint}
\onehalfspacing

@@

\textbf{\huge{}An Adapted Laplacian Operator For Hybrid Quad/Triangle
Meshes}{\huge \par}

@@

\textbf{\large{}Alexander Pinzón Fernández}{\large \par}

@@

Facultad de Ingeniería, Departamento de Sistemas e Industrial

{\small{}Grupo de Investigación CIM@LAB}{\small \par}

@@

{\small{}A thesis submitted in partial fulfillment of the requirements
for the degree of:}{\small \par}

@@

{\small{}Advisor:}\\
{\small{}Eduardo Romero Castro , Ph.D.}{\small \par}

{\small{}\vspace{1.5cm}
}{\small \par}

{\small{}Research Area:}\\
{\small{}Computer Graphics}{\small \par}

{\small{}\vspace{2cm}
}{\small \par}

{\small{}Universidad Nacional de Colombia}\\
{\small{}Facultad de Ingeniería, Departamento de Sistemas e Industrial}\\
{\small{}Grupo de Investigación CIM@LAB}\\
{\small{}Bogotá, Colombia}\\
{\small{}2014}{\small \par}

@@

{\small{}\vspace{4cm}
}{\small \par}

\noindent \begin{flushright}
\begin{minipage}[t]{8cm}%
{\small{}A Beatriz y Campo Elias mis padres que siempre me dieron
la libertad de escoger, con su comprensión y apoyo me permitieron
dedicar mi tiempo a la ciencia.}{\small \par}

{\small{}\vspace{1cm}
}{\small \par}

{\small{}A mis padres}{\small \par}

{\small{}\vspace{1cm}
}{\small \par}

@@

Campo Elias Pinzón Rojas%
\end{minipage}
\par\end{flushright}

@@

\textbf{\LARGE{}Acknowledgment}{\LARGE \par}

\addcontentsline{toc}{chapter}{\protect\numberline{}Acknowledgement}

@@

I wold like to thank my advisor professor Eduardo Romero and the CIM\&LAB
research group for their support in this thesis.

{\small{}\vspace{1cm}
}{\small \par}

@@

{\small{}\vspace{1cm}
}{\small \par}

This work was supported in part by the Blender Foundation, Google
Summer of code program 2012 and 2013.

@@

\textbf{\LARGE{}Abstract}{\LARGE \par}

\addcontentsline{toc}{chapter}{\protect\numberline{}Abstract}

In the last two decades three-dimensional modeling methods used by
artists have been evolving and developing rapidly thanks to the use
of vector operators of differential geometry such as the Laplacian
operator. This operator allows to model in a simple way the behavior
of complex applications such as noise reduction, enhancement, remeshing,
UV mapping, posing and skeletonization, among others. The Laplacian
operator is theoretically defined in a continuous and smooth domain
named manifold. In practice manifolds are often approximated by discrete
polygon meshes composed by triangles and quadrangles which represent
the real world three-dimensional objects with which the artists work.
In these meshes spectral structure is calculated using a discrete
Laplacian operator, i.e. the discrete version of the Laplacian operator
given by Pinkall in 1993. This approach only worked with triangle
meshes. In 2011 Xiong extended the operator to work exclusively with
quad meshes. This thesis proposes an original extension of the Laplacian
operator that allows working with hybrid meshes composed by triangles
and quadrangles.

Along with the operator, this work presents new sculpting and modeling
applications based on enhancement. Additionally applications on subdivision
surfaces using smoothing, mesh posing using differential coordinates
and skeletonization using iterative contraction are develop. This
series of applications demonstrates the quality, predictability and
flexibility of the proposed operator.

The proposed operator was successfully used in new software tools
in real production environment within 3D computer graphics software
Blender. Currently these tools are available as open source software.

\textbf{\LARGE{}Resumen}{\LARGE \par}

En las dos últimas décadas los métodos de modelado tridimensional
utilizadas por los artistas han ido evolucionando y desarrollándose
rápidamente, en parte gracias al uso de operadores vectoriales de
geometría diferencial, como el operador de Laplace. Este operador
permite modelar de una manera sencilla el comportamiento de aplicaciones
complejas tales como la reducción de ruido, realce, remallado, mapeado
UV, posado y esqueletonización, entre otros. Este operador Laplaciano
es teóricamente definido en un dominio continuo y suave llamado variedad,
las variedades son a menudo aproximadas por mallas discretas de polígonos
compuestas por triángulos y cuadrángulos que a su vez representan
objetos tridimensionales del mundo real que los artistas trabajan.
En estas mallas se calcula la estructura espectral con el uso de algún
operador Laplaciano discreto, la versión discreta del operador Laplaciano
propuesta por Pinkall en el 1993 trabaja únicamente con mallas compuestas
por triángulos, y la de Xiong en el 2011 trabaja exclusivamente con
cuadrángulos. Esta tesis propone una extensión original del Operador
Laplaciano que permite trabajar con mallas híbridas compuestas por
triángulos y cuadrángulos.

@@

El operador propuesto fue usado con exitoso en las nuevas herramientas
del software para gráficos 3D por computadora Blender. Actualmente
estas herramientas están disponibles como programas de código abierto.

{\small{}\vspace{1cm}
}{\small \par}

\textbf{\small{}Keywords: laplacian operator; smooth; enhance; sculpting;
subdivision surface}{\small \par}

@@

The discrete versions of the Laplace Beltrami Operator have been used
in the last years for the development of new geometric modeling tools.
Pinkall \cite{Pinkall1993} introduced the cotangent version of the
Laplace operator, that allowed finding the minimal surface when computing
a discrete harmonic map with the Laplacian operator. This version
has been widely studied and applied in various problems of computer
geometric modeling. This type of operator was defined over manifolds,
i.e. continuous domains homeomorphic to $\mathbb{R}^{n}$ that are
represented in pratice by polygon meshes. These polygons are generally
composed of triangles and quadrangles. While working with Laplacian
operator in this hybrid composition is not a mathematical challenge,
most research only uses meshes composed by triangles \cite{Pinkall1993,Desbrun1999,Meyer2003,Sorkine2004,Au2008,Belkin2008,Hahne2006}.
In recent studies \cite{Liu2008,Xiong2011}, the Laplacian operator
may be use in meshes composed exclusively by quadrangles. However,
from artistic point of view, the topology and the way the edges, triangles
and quadrangles are distributed directly affects the processes of
animation, interpolation, texturing, etc., as discussed by \cite{Mullen2007}
who uses a manual connection of a pair of vertices to perform animation
processes and interpolation. It is then of paramount importance to
develop operators that easily interact with such meshes, eliminating
the need of preprocessing the mesh to convert it to triangles and
change the original topology.

Presently there are available modeling techniques able to generate
a variety of realistic shapes \cite{Botsch2006}. Editing techniques
have evolved from affine transformations to advanced tools like sculpting
\cite{Coquillart1990,Galyean1991,Stanculescu2011}, editing, creation
from sketches \cite{Igarashi1999,Gonen2012}, and complex interpolation
techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark based methods
however require to interact with a minimum number of control points
for any operation to be efficient, or in other words, a unicity condition
is introduced by demanding a smooth surface after any of these shape
operations. Hence, traditional modeling methods for subdividing surfaces
from coarse geometry have become widely popular \cite{Catmull1978,Stam1998}.
These works have generalized a uniform B-cubic spline knot insertion
to meshes. Some of these adds some type of control; for instance with
the use of creases to produce sharp edges \cite{DeRose1998} or the
modification of some vertex weights to locally control the zone of
influence \cite{Biermann2000}. Nevertheless  these methods are difficult
to use as they require a large number of parameters and a very tedious
customization.

On the other hand, the proposed applications requires a single parameter
that controls the global curvature, which is used to maintain realistic
shapes, creating a family of different versions of the same object
and therefore preserving the detail of the original model and a realistic
appearance.

The shape inflation and shape exaggeration can thus be used as a type
of brush in the sculpting process. When inflating a shape with other
brushes the former ends up losing detail when moving vertices \cite{Stanculescu2011}.
In contrast, the presented enhance method inflates a mesh by moving
the vertices towards the reverse curvature direction, conserving the
shape and sharp features of the model.

@@

This work presents an extension of the Laplace Beltrami Operator for
hybrid quad/triangle meshes that have a larger mesh functionality
spectrum than common triangular or quadrangular meshes. The method
eliminates the need of preprocessing and allows preservation of the
original topology. Along with this operator, we propose a method to
generate a family of parameterized shapes, in a robust and predictable
way. This method enables customization of the smoothness and curvature
obtained during the subdivision surfaces process. Finally, a new brush
for inflating the silhouette mesh features in modeling and sculpting
is proposed.

The work is organized as follows: Chapter \ref{chap:Mathematical-foundation}
presents works related to the Laplacian operator, applications in
digital sculpting, deformation, and offsetting methods for polygonal
meshes. It also describes the theoretical framework of the Laplacian
operator for polygon meshes; In chapter \ref{chap:SibgrapiPaper},
we show the extension of the Laplacian Operator for hybrid meshes
and the applications of shape inflation ,subdivision of surfaces and
sculpting; In chapter \ref{sub:Laplacian-Smooth}, we present an application
for mesh smoothing of the the Laplacian operator extension proposed
implemented in a well known software for computer modelling. Finally
in chapter \ref{sub:Laplacian-Deform}, we present a successfull application
for mesh deformation and model re-posing based on differential coordinates
and the adaptation of this method to work with our Laplacian operator
extension.

\chapter{Mathematical Foundation and Background\label{chap:Mathematical-foundation}}

This chapter studies basic mathematical foundation on differential
geometry to understand the differential operators and the Laplace
Beltrami operator.

The differential geometry studies curvatures and geodesics \cite{Hahne2006}.
These differential operators show a deep relationship between the
geometry (curvatures, geodesics) and topology of the manifold. They
have been commonly used in computer geometric modelling applications
over the last years \cite{Rosenberg1997,Alexa2011}.

\section{Related work}

Many tools have been developed for modeling based on the Laplacian
mesh processing. These tools preserve the surface geometric details
when using laplacian operators for different processes such as smoothing,
enhancing, free-form deformation, fusion, morphing and other applications
\cite{Ranjan2012}.

@@

Where $N_{1}$is the 1-ring neighborhood, $\alpha$ and $\beta$ are
the opposite angles to edge between vertex $i$ and vertex $j$. In
this work the discrete laplacian operator is used to find the minimal
surface based on minimization energy strategy using the Dirichlet's
energy of the function $u$ over a manifold represented by triangulated
mesh $\Omega$.

@@

Taubin \cite{Taubin1995} treats for the first time the problem of
noise reduction in digital polygonal meshes from signal processing
point of view. He extends Fourier analysis to signals defined on polygonal
meshes and observes that Fourier transform is a decomposition of the
signal into eigenvectors of the Laplacian operator and reconstructs
the signal with a linear combination of these eigenvectors. Desbrun
et al. \cite{Desbrun1999} consider the same approach of Taubin, but
they use a curvature normal ($\bar{\kappa}\mathbf{n}$) based on cotangent
Laplace operator version for noise reduction over a diffusion process.
This is the most famous and popular Laplace Beltrami operator discretization
\cite{Liu2008}, many works for mesh smoothing and fairing have been
developed based on his Laplace Beltrami Operator (LBO) discretization
\cite{Desbrun2000,Meyer2003,Schneider2001,Nealen2006}:

@@

where $A$ is the area surrounding vertex $i$. This laplacian operator
$L$ was used to reduce the noise in a mesh $X$ over a diffusion
process.

The convergence of the Laplace Beltrami operator has been very important
in fields such as numerical analysis, given its implications in the
simulation process and geometric partial differentials equations.
Xu et al. \cite{Xu2004} established the convergence of several discrete
Laplace Beltrami operators over triangulated meshes with numerical
results that support the theoretical analysis. Over quadrilateral
meshes Liu et al. \cite{Liu2008} present a discrete Laplace Beltrami
Operator based on a bilinear interpolation and its convergence over
meshes composed only by quads.

In the work of Sorkine \cite{Sorkine2006} the laplacian operator
was used to re-pose a mesh while preserving geometry details of the
surface. The details were stored in differential coordinates $\delta_{i}$
for every vertex $v_{i}$.

@@

The differential coordinates represent the difference between the
absolute coordinate of $v_{i}$and the center of mass of its immediate
neighbors.

Offset methods for polygon meshing, based on the curvature defined
by the Laplace Beltrami operator, have been developed. These methods
adjust the shape offset by a constant distance, with high precision.
Nevertheless, these methods fail to conserve sufficient detail because
of the smoothing, a crucial issue which depends on the offset size
\cite{Zhuo2012}. In volumetric approaches, in case of point-based
representations, the offset boundary computation is based on the distance
field and therefore when calculating such offset, the topology of
the model may be different to the original \cite{Chen2011}.

Gal et al. \cite{Gal2009} propose automatic feature detection and
shape edition with feature inter-relationship preservation. They define
salient surface features like ridges and valleys, characterized by
their first and second order curvature derivatives (see \cite{Ohtake2004})
and angle-based thresholds. Likewise, curves have been also classified
as planar or non-planar, approximated by lines, circles, ellipses
and other complex shapes. In each case, the user defines an initial
change over several features which is propagated towards other features,
based on the classified shapes and the inter-relationships between
them. This method works well with objects that have sharp edges, composed
of basic geometric shapes such as lines, circles or ellipses. However,
the method is very limited when models are smooth since it cannot
find the proper features to edit.

Digital sculpting has been traditionally approached either under a
polygonal representation or a voxel grid-based method. Brushes for
inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
In grid-based sculpting, some other operations have allowed to add
or remove voxels since production of polygonal meshes require a processing
of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
from the difficulty of maintaining the surface details during larger
scale deformations.

In the literature, several studies have described the skeleton extraction
systems and different metrics that identify appropriate methods given
a specific application \cite{Attali2007}. One of the best methods
reported in the literature for the extraction of the skeleton is the
Laplacian smoothing method given its advantages of homotopy representation
and hierarchical connections between parts. The skeleton extraction
methods permit simplifying the dimension of the object preserving
the topological structure \cite{Cornea2007}, Au et. al. \cite{Au2008}
present a skeleton extraction method based on iterative smoothing-contraction.
In this method several constraints are used to warrant that the process
converges to a skeleton formed by branches and joints. The constraints
are based on laplacian operator; the low frequencies of the mesh are
preserved with the use of an attractor to the original mesh, while
the iterative smoothing process removes high frequencies.

@@

Our work is related to manifolds that represent a surface in an three-dimensional
Euclidean Space. This manifolds are homeomorphic to $\mathbb{R}^{2}$.

The manifolds are represented by polygonal meshes with points connected
by triangles and quads.

@@

\chapter{Shape Inflation With an Adapted Laplacian Operator For Hybrid Quad/Triangle
Meshes\label{chap:SibgrapiPaper}}

\noindent \begin{center}
Alexander Pinzón, Eduardo Romero\\
Cimalab Research Group\\
Universidad Nacional de Colombia\\
Bogota-Colombia\\
Email: apinzonf@unal.edu.co, edromero@unal.edu.co
\par\end{center}

\protect\caption{\label{PAPER:fig:Spectrum}A set of 48 successive shapes enhanced,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}
\end{figure}

This paper was accepted and presented in the Brazilian Symposium on
Computer Graphics and Image Processing SIBGRAPI 2013. The conference
was held on August 5-8 of 2013, in the city of Arequipa, Perú \cite{Pinzon2013}.

\section*{Abstract}

This paper proposes a novel modeling method for a hybrid quad/triangle
mesh that allows to set a family of possible shapes by controlling
a single parameter, the global curvature. The method uses an original
extension of the Laplace Beltrami operator that efficiently estimates
a curvature parameter which is used to define an inflated shape after
a particular operation performed in certain mesh points. Along with
the method, this work presents new applications in sculpting and modeling,
with subdivision of surfaces and weight vertex groups. A series of
graphics examples demonstrates the quality, predictability and flexibility
of the method in a real production environment with software Blender.
\begin{description}
\item [{keywords-}] laplacian smooth; curvature; sculpting; subdivision
surface
\end{description}

\section{Introduction}

Over the last years several, modeling techniques able to generate
a variety of realistic shapes, have been developed \cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a small number of control
points for any operation to be efficient, or in other words, a unity
 condition is introduced by demanding a smooth surface after any of
these shape operations. Hence, traditional modeling methods for subdividing
surfaces from coarse geometry have become widely popular \cite{Catmull1978,Stam1998}.
These works have generalized a uniform B-cubic spline knot insertion
to meshes, some of them adding some type of control, for instance
with the use of creases to produce sharp edges \cite{DeRose1998},
or the modification of some vertex weights to locally control the
zone of influence \cite{Biermann2000}. Nevertheless these methods
are difficult to deal with since they require a large number of parameters
and a very tedious customization. Instead, the presented method requires
a single parameter that controls the global curvature, which is used
to maintain realistic shapes, creating a family of different versions
of the same object and therefore preserving the detail of the original
model and a realistic appearance.

Interest in meshes composed of triangles and quads has lately increased
because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
Nowadays, many artists use a manual connection of a couple of vertices
to perform animation processes and interpolation \cite{Mullen2007}.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles. The shape inflation and shape exaggeration
can thus be used as such brush in the sculpting process, when inflating
a shape since current brushes end up by losing detail when moving
vertices \cite{Stanculescu2011}. In contrast, the presented method
inflates a mesh by moving the vertices towards the reverse curvature
direction, conserving the shape and sharp features of the model.

\subsection*{Contributions }

This work presents an extension of the Laplace Beltrami operator for
hybrid quad/triangle meshes, representing a larger mesh spectrum from
what has been presented so far. The method eliminates the need of
preprocessing and allows preservation of the original topology. Likewise,
along with this operator, it is proposed a method to generate a family
of parametrized shapes, in a robust and predictable way. This method
enables customization of the smoothness and curvature, obtained during
the subdivision surfaces process. Finally, it is proposed a new brush
for inflating the silhouette mesh features in modeling and sculpting.

This work is organized as follows: Section \ref{sec:Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth},
it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{PAPER:sec:Proposed-Method}, it
is presented the method for shape inflation and applications of subdivision
of surfaces and sculpting; finally some Laplacian operator results,
to hybrid quad/triangle meshes are graphically shown as well as results
of the shape inflation applications in sculpting, subdivision and
modeling.

\section{Related work\label{sec:Related-work}}

Many tools have been developed for modeling, based on the Laplacian
mesh processing. Thanks to the advantages of the Laplacian operator,
these different tools preserve the surface geometric details when
using them for different processes such as free-form deformation,
fusion, morphing and other applications \cite{Sorkine2004}.

\cite{Gal2009} proposes automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characterized by their first
and second order curvature derivatives, see \cite{Ohtake2004}, and
angle-based threshold. Likewise, curves have been also classified
as planar or non-planar, approximated by lines, circles, ellipses
and other complex shapes. In such case, the user defines an initial
change over several features which are propagated towards other features,
based on the classified shapes and the inter-relationships between
them. This method works well with objects that have sharp edges, composed
of basic geometric shapes such as lines, circles or ellipses. However,
the method is very limited when models are smooth since it cannot
find the proper features to edit.

Digital sculpting has been traditionally approached either under a
polygonal representation or a voxel grid-based method. Brushes for
inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
In grid-based sculpting, some other operations have allowed to add
or remove voxels since production of polygonal meshes require a processing
of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
from the difficulty of maintaining the surface details during larger
scale deformations.

\section{Laplacian Smooth\label{sec:Laplacian-Smooth}}

Computer objects, reconstructed from the real world, are usually noisy.
Laplacian Smooth techniques allow a proper noise reduction on the
mesh surface with minimal shape changes, while still preserving a
desirable geometry as well as the original shape.

Many smoothing Laplacian functionals regularize the surface energy
by controlling the total surface curvature $S$.

\noindent \begin{center}
$E\left(S\right)=\int_{S}\kappa_{1}^{2}+\kappa_{2}^{2}dS$
\par\end{center}

Where $\kappa_{1}$ and $\kappa_{2}$ are the two principal curvatures
of the surface $S$.

@@
